**Preprinting Microbiology**

### 2017-01-30 submission/Schloss_PrePrints_mBio_2017.Rmd
Light editing

***Microbiology anecdotes.*** The peer-review editorial process can be lengthy and adversarial. In contrast, preprints represent a rapid and potentially collaborative method for disseminating research. Several from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints. First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies. Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; the number of Zika virus-related publications is now over 1,700. During this time, more than 110 Zika virus-related preprints have been posted at *bioRxiv*. Any manuscript that was published likely went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus. However, those that posted their work as a preprint were able to instantly disseminate their methods and results.

>>>>

***Microbiology anecdotes.*** The peer-review editorial process can be lengthy and adversarial. In contrast, preprints represent a rapid and potentially collaborative method for disseminating research. Several from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints. First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies. Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; the number of Zika virus-related publications is now over 1,700. During this time, more than 110 Zika virus-related preprints have been posted at *bioRxiv*. Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus. In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly.
